\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewriting first empirical part

After obtaining the base forecasts these are reconciled using three different projection methods: OLS, MinT and WLS.  {\color{blue}For MinT, the shrinkage estimator of \cite{Schafer2005} is used, i.e., $\bm{W}^{\text{MinT}} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
\begin{equation*}
\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
\end{equation*}
where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.  For WLS, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$.} Squared forecast errors are computed for each series and aggregated across the entire hierarchy; i.e., we compute the loss function described in Section~\ref{sec:orthogonal}. We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate. We also include bottom-up forecasts in this comparison for completeness.

>>>>

{\color{blue} For each replication and for method $q$, the total squared error (TSE), is computed as
	\begin{equation*}
	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
	\end{equation*}
	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider a loss function based on a generalised Euclidean distance of the form
\begin{equation*}
	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
	\end{equation*}
	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
}

After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} WLS, MinT and GMinT.   For MinT and GMinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.  That is $\bm{\Sigma} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
	\begin{equation*}
	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
	\end{equation*}
	where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.  For WLS and GMinT, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$ CHANGE DEPENDING ON FINAL CHOICE OF W.  For both loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
